\documentclass[11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}
[\titlerule]

\begin{document}

% -----------------------
% HEADER
% -----------------------

\begin{center}
{\LARGE \textbf{ Satyam Kumar Mishra }} \\

satyamkumarmishra2005@gmail.com



| \href{https://linkedin.com/in/satyam}linkedin.com/in/satyam

| \href{https://github.com/satyamkumarmishra2005}github.com/satyamkumarmishra2005


\end{center}

\vspace{6pt}

% -----------------------
% SUMMARY
% -----------------------



\section*{Summary}

Backend Engineer specializing in building scalable, high-availability systems with Java and Spring Boot. Experienced in microservices architecture, event-driven design with Kafka, and cloud-native deployments on Kubernetes and AWS. Passionate about solving complex distributed systems challenges, API integrations, and building resilient infrastructure with 99.9\%+ uptime.



% -----------------------
% SKILLS
% -----------------------



\section*{Technical Skills}

\begin{tabular}{p{0.32\textwidth} p{0.32\textwidth} p{0.32\textwidth}}


Java & Spring Boot & RESTful APIs  \\


SQL & PostgreSQL & MySQL  \\


Git & Maven & Microservices Architecture  \\


Apache Kafka & RabbitMQ & Docker  \\


Kubernetes & AWS & Spring Security  \\


JWT & OAuth2 & Spring Cloud  \\


Spring Data JPA & Microservices & Event Sourcing  \\


Asynchronous Processing & JDBC & Transaction Management  \\


Keycloak & Role-Based Access Control (RBAC) & Helm  \\


CI/CD & API Gateway & Service Discovery (Eureka)  \\


High Availability & Fault Tolerance &   \\



\end{tabular}



% -----------------------
% EXPERIENCE
% -----------------------



% -----------------------
% PROJECTS
% -----------------------



\section*{Projects}



\textbf{ Eazy Bank – Microservices Banking Platform }
 (\href{https://GitHub}GitHub) 

\begin{itemize}


\item Architected a cloud-native digital banking system with 4 independently deployable microservices (Accounts, Cards, Loans, Messaging), processing transactional workflows leveraging domain-driven design principles.

\item Implemented centralized configuration management with Spring Cloud Config Server, enabling zero-downtime deployments and environment-specific configurations across distributed services.

\item Utilized event-driven architecture with Apache Kafka for asynchronous inter-service communication, ensuring loose coupling and system resilience under high transaction volumes.

\item Deployed on Kubernetes with self-healing capabilities, rolling updates, and horizontal pod autoscaling to achieve 99.9\% service availability.


\end{itemize}



\textbf{ RapidAid – Real-time Emergency Response System }
 (\href{https://GitHub}GitHub) 

\begin{itemize}


\item Developed a microservices platform for real-time incident reporting and automated responder allocation, achieving sub-second response times.

\item Integrated Keycloak for enterprise-grade OAuth2/JWT authentication and Role-Based Access Control (RBAC) across multiple services.

\item Designed event-driven workflows using Kafka to decouple incident intake, routing logic, and notification delivery, improving system scalability and fault tolerance.

\item Implemented state machine-based responder lifecycle management with automated notifications and consistency guarantees under concurrent incident loads.


\end{itemize}



\textbf{ MediSort – Medicine Management Backend }
 (\href{https://GitHub}GitHub) 

\begin{itemize}


\item Built a RESTful backend system for prescription management, incorporating intelligent OCR processing from PDFs/images and structured metadata extraction.

\item Engineered a scheduled reminder system with escalation workflows and acknowledgment tracking to improve medication adherence rates.

\item Deployed on AWS infrastructure utilizing EC2 compute instances, RDS for PostgreSQL data persistence, and Route 53 for DNS-based service routing.

\item Integrated Cloudinary CDN for secure document storage with API-based access control and optimized content delivery at scale.


\end{itemize}





% -----------------------
% EDUCATION
% -----------------------



\section*{Education}



\textbf{ Bachelor of Technology in Computer Science and Engineering }

Dronacharya College of Engineering Gurugram, Haryana

{\small Aug 2023 - Aug 2027}

\vspace{4pt}





% -----------------------
% CERTIFICATIONS
% -----------------------



\end{document}